Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-06 docs/evol.tex
moved pfs to build succesfully
improved figure

Although there seems to be zero tendency taken over all versions of
all projects together, the situation might be different in individual
projects. We therefore performed Spearman correlations between bug
counts and version ordinals in all projects we examined. These paint a
different picture from the above table, shown in
Figure~\ref{fig:bugsversioncorr}. The spike in point zero is explained
by the large number of projects for which no correlation could be
established---note that the scale is logarithmic.

@@

\begin{figure*}
  \centering
  \includegraphics[scale=0.4]{bugsversionscorr.pdf}
  \caption{Histograms of correlations between bug counts and version
    ordinals per project}
  \label{fig:bugsversionscorr}
\end{figure*}

>>>>

Although there seems to be zero tendency taken over all versions of
all projects together, the situation might be different in individual
projects. We therefore performed Spearman correlations between bug
counts and version ordinals in all projects we examined. These paint a
different picture from the above table, shown in
Figure~\ref{fig:bugsversionscorr}. The spike in point zero is explained
by the large number of projects for which no correlation could be
established---note that the scale is logarithmic.

@@

\begin{figure*}
  \centering
  \includegraphics[scale=0.4]{bugsversionscorr}
  \caption{Histograms of correlations between bug counts and version
    ordinals per project. In brackets the total population size and
    the number of no correlation instances.}
  \label{fig:bugsversionscorr}
\end{figure*}
